Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
describe metrics

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
source code of the method is available at
\url{https://github.com/asutera/kaggle-connectomics} under 3-clause BSD
license.

@@

\section{Experiments}
\subsection{Accuracy assessment protocol}
% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$.

% Metrics : ROC AUC an AUPRC
% We assess the accuracy of the neuronal network

>>>>

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
source code of the method is available at
\url{https://github.com/asutera/kaggle-connectomics} under BSD 3-clauses
license.

@@

\section{Experiments}
% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$.

% Metrics : ROC AUC an AUPRC
The network inference task can be viewed as a binary classification task
where one have to correctly classified the presence or the absence of edges
in the connectivity graph. Given the ground true network
$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
context, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
which is also called the confusion matrix.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
as a function of the false positive rate
$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
curve obtained by varying the threshold
$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
which is an information retrieval measure.
